Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2020-02-19 ms/spaceness.tex
added reviewer acknowledgements, misc typo fixes

Also note that $\sigma$ controls the dispersal of offspring away from only \emph{one} parent \llabel{ll:sigma_effective}
(e.g., the seed parent for plants),
while the usual population genetics definition of dispersal distance
involves the distance to a randomly chosen one of the two parents.
(thus taking into account the distance from pollen parent as well).
This second component -- the distance between mates --
has in our simulations a distribution that is of order $\sigma$ but that depends on the population's patchiness.
If both between-mate distance and dispersal distance has variance $\sigma^2$ along each axis,
then the mean squared distance to a randomly chosen parent along that axis would be
$(\sigma^2 + 2 \sigma^2)/2 = 3 \sigma^2 /2$.
Also note that Wright's definition of neighborhood size should rightly use the \emph{effective}
dispersal distance, i.e., the mean squared displacement along an axis
between parent-child pairs found moving back along a lineage \citep{barton2002neutral}.
Nonetheless, we use $\sigma$ and $\rho$ as defined here to compute $N_W$
because these quantities are more easily observable in practice than their ``effective'' versions.
(Also, note that effective population density is lower than the actual population density,
while the $\sigma$ we use is an underestimate,
so our numbers may be close to the ``effective'' values used in theory.

@@

\section{Acknowledgements}
We thank Brandon Cooper, Matt Hahn, Doc Edge, and others for reading and thinking about this manuscript. 
% We thank the Hearth for having such good, nearby coffee, and
% Falling Sky Brewing for creative support during manuscript drafting.
CJB and ADK were supported by NIH award R01GM117241.

>>>>

Also note that $\sigma$ controls the dispersal of offspring away from only \emph{one} parent \llabel{ll:sigma_effective}
(e.g., the seed parent for plants),
while the usual population genetics definition of dispersal distance
involves the distance to a randomly chosen one of the two parents.
(thus taking into account the distance from pollen parent as well).
This second component -- the distance between mates --
has in our simulations a distribution that is of order $\sigma$ but that depends on the population's patchiness.
If both between-mate distance and dispersal distance has variance $\sigma^2$ along each axis,
then the mean squared distance to a randomly chosen parent along that axis would be
$(\sigma^2 + 2 \sigma^2)/2 = 3 \sigma^2 /2$.
Also note that Wright's definition of neighborhood size should rightly use the \emph{effective}
dispersal distance, i.e., the mean squared displacement along an axis
between parent-child pairs found moving back along a lineage \citep{barton2002neutral}.
Nonetheless, we use $\sigma$ and $\rho$ as defined here to compute $N_W$
because these quantities are more easily observable in practice than their ``effective'' versions.
We also note that effective population density is lower than the actual population density,
while the $\sigma$ we use is an underestimate,
so our numbers may be close to the ``effective'' values used in theory.

@@

\section{Acknowledgements}
We thank Brandon Cooper, Matt Hahn, Doc Edge, and others for reading and thinking about this manuscript. 
Three anonymous reviewers and the suggestions from editors of GENETICS significantly improved the final manuscript. 
CJB and ADK were supported by NIH award R01GM117241.
